Technical Report

### 2018-03-19 fully-abstract-comp/technical-report.tex
Fix typo.
First stab at the trusted value relation.
Add notes about illegal source program behavior we need to exclude.

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
\[
  \lrv(W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \;\middle|\; i \in \ints \right\}\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{c_S},\\ \sealed{\sigma,\vsc_T} \endarray\right)} \;\middle| \;
    \begin{array}{l}
      \npair{(\src{c_S},\sealed{\sigma,\vsc_T})} \in \lrp(W) \wedge \\
      \exists r \in \dom(\pwheap)\ldotp \pwheap(r) = (\pure,s,\_,\_,\_,H_\sigma) \tand \\
      \stpair[.]{c_S}{\vsc_T} \in H_\sigma \; s \; \sigma \; W\wedge \\
      \forall W' \future W, W_o, n' < n, \stpair[.]{c_S'}{\vsc'_T} \in H_\sigma \; s \; \sigma \; W_o \ldotp \\
      \quad \npair[n']{\src{c_S},\src{c_S'},\sealed{\sigma,\vsc_T},\sealed{\sigma,\vsc_T'}} \in \lrexj(W'\oplus W_o) \wedge \\
      \quad \npair[n']{\src{c_S'},\src{c_S},\sealed{\sigma,\vsc_T'},\sealed{\sigma,\vsc_T}} \in \lrexj(W' \oplus W_o)
    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    \; \middle| \;
    \exists r \in \dom(\pwheap) \ldotp \forall \ldotp \pwheap(r) = (\pure,s,\_,\_,\_,H_\sigma) \tand H_\sigma\; s \; \sigma \nequal \lrv
    \right\} \cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\;
    \begin{array}{l}
      \npair{(\src{\stkptr{\perm,\baddr,\eaddr,\aaddr}}, ((\perm,\linear),\baddr,\eaddr,\aaddr))} \in \lrp(W) \wedge \\
      \begin{array}{r l l}
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \stackReadCond{W} \wedge \\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \stackWriteCond{W}
      \end{array}
    \end{array}
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{l}
      \npair{(\src{((\perm,\lin),\baddr,\eaddr,\aaddr)}, ((\perm,\lin),\baddr,\eaddr,\aaddr))} \in \lrp(W) \wedge \\
      \begin{array}{r l l }
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \readCond{\lin,W} \wedge\\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \writeCond{\lin,W} \wedge\\
        % we are excluding rwx pointers.
        \perm \neq \rwx \wedge \\
        % \perm = \rwx &\Rightarrow& \array[t]{l}\npair{(\{\rwx,\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge \\
        %                            \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W} \endarray\\
        \perm = \rx &\Rightarrow& \array[t]{l}\npair{(\{\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge\\
                                  \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}\endarray
      \end{array}
    \end{array}
    \right\}
  \end{array}
\]

@@

\begin{definition}[Never pass trusted seals accross the trusted-untrusted boundary]
  A configuration $\src{\Phi}$ is said to use linker seals properly in $\ta$ for $n$ steps iff\\
  for all $i \leq n$, if
  \[
    \src{\Phi} \nstep[i] \src{\Phi'} \step \src{\Phi''}
  \]
  and $\src{\Phi'}$ is in $\ta$ and $\src{\Phi''}$ is not in $\ta$ and
  $\src{\Phi}.\reg(r_i) = \seal{\sigma_b,\sigma_e}$ and
  \dominique{TODO: $\sigma_b,\sigma_e$ contains a seal that was put in $\Phi$ by the linker.}
\end{definition}

>>>>

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
\[
  \lrv(W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \;\middle|\; i \in \ints \right\}\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{c_S},\\ \sealed{\sigma,\vsc_T} \endarray\right)} \;\middle| \;
    \begin{array}{l}
      \npair{(\src{c_S},\sealed{\sigma,\vsc_T})} \in \lrp(W) \wedge \\
      \exists r \in \dom(\pwheap)\ldotp \pwheap(r) = (\pure,s,\_,\_,\_,H_\sigma) \tand \\
      \stpair[.]{c_S}{\vsc_T} \in H_\sigma \; s \; \sigma \; W\wedge \\
      \forall W' \future W, W_o, n' < n, \stpair[.]{c_S'}{\vsc'_T} \in H_\sigma \; s \; \sigma \; W_o \ldotp \\
      \quad \npair[n']{\src{c_S},\src{c_S'},\sealed{\sigma,\vsc_T},\sealed{\sigma,\vsc_T'}} \in \lrexj(W'\oplus W_o) \wedge \\
      \quad \npair[n']{\src{c_S'},\src{c_S},\sealed{\sigma,\vsc_T'},\sealed{\sigma,\vsc_T}} \in \lrexj(W' \oplus W_o)
    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    \; \middle| \;
    \exists r \in \dom(\pwheap) \ldotp \pwheap(r) = (\pure,s,\_,\_,\_,H_\sigma) \tand H_\sigma\; s \; \sigma \nequal \lrv
    \right\} \cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\;
    \begin{array}{l}
      \npair{(\src{\stkptr{\perm,\baddr,\eaddr,\aaddr}}, ((\perm,\linear),\baddr,\eaddr,\aaddr))} \in \lrp(W) \wedge \\
      \begin{array}{r l l}
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \stackReadCond{W} \wedge \\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \stackWriteCond{W}
      \end{array}
    \end{array}
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{l}
      \npair{(\src{((\perm,\lin),\baddr,\eaddr,\aaddr)}, ((\perm,\lin),\baddr,\eaddr,\aaddr))} \in \lrp(W) \wedge \\
      \begin{array}{r l l }
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \readCond{\lin,W} \wedge\\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \writeCond{\lin,W} \wedge\\
        % we are excluding rwx pointers.
        \perm \neq \rwx \wedge \\
        % \perm = \rwx &\Rightarrow& \array[t]{l}\npair{(\{\rwx,\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge \\
        %                            \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W} \endarray\\
        \perm = \rx &\Rightarrow& \array[t]{l}\npair{(\{\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge\\
                                  \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}\endarray
      \end{array}
    \end{array}
    \right\}
  \end{array}
\]

\[
  \lrvtrusted(W) =
  \begin{array}[t]{l}
    \lrv(W)\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    \; \middle| \;
    \exists r \in \dom(\pwheap) \ldotp \pwheap(r) =_n \text{TODO: code region for trusted code}
    \right\} \cup \\
  \end{array}
\]

@@

\begin{definition}[Never pass trusted seals accross the trusted-untrusted boundary]
  A configuration $\src{\Phi}$ is said to use linker seals properly in $\ta$ for $n$ steps iff\\
  for all $i \leq n$, if
  \[
    \src{\Phi} \nstep[i] \src{\Phi'} \step \src{\Phi''}
  \]
  and $\src{\Phi'}$ is in $\ta$ and $\src{\Phi''}$ is not in $\ta$ and
  $\src{\Phi}.\reg(r_i) = \seal{\sigma_b,\sigma_e}$ and
  \dominique{TODO: $\sigma_b,\sigma_e$ contains a seal that was put in $\Phi$ by the linker.}
  \dominique{TODO: Also not allowed: passing a capability to a code area that points (a.o.) to a memory location containing a seal like the one above.}
  \dominique{TODO: Also not allowed: storing a seal or a code capability in memory.}
  \dominique{TODO: Also not allowed: sealing such a value with a seal that you do not own.}
\end{definition}
